Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
yny adhesion
yny adhesion up to page 9

\begin{abstract}
The dynamics of an adhesive two-dimensional vesicle doublet under
various flow conditions is investigated numerically using a high-order,
adaptive-in-time boundary integral method. In a quiescent flow, two
nearby vesicles move slowly towards each other under the adhesive
potential, pushing out fluid between them to form a vesicle doublet at
equilibrium. A lubrication analysis on such draining of a thin film
gives the dependencies of draining time on adhesion strength and
separation distance that are in good agreement with numerical results.
%
In a microfluid trap where the stagnation of an extensional flow is
dynamically placed in the middle of a vesicle doublet through an active
control loop, novel dynamics of a vesicle doublet is observed. Numerical
simulations show that there exists a critical extensional flow rate
above which adhesive interaction is overcome by the diverging stream,
thus providing a simple method to measure the adhesion strength between
two vesicle membranes. 
%
In a planar shear flow, numerical simulations reveal that a vesicle
doublet may form provided that the adhesion strength is sufficiently
large at a given vesicle reduced area. Once a doublet is formed, the
effective shear viscosity of a dilute suspension of vesicle doublets is
found to be a function of  reduced area.  Results from these numerical
studies and analysis shed light on the hydrodynamic and rheological
consequences of adhesive interactions between vesicles in a viscous
fluid.
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[PACS numbers]
%May be entered using the \verb+\pacs{#1}+ command.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item. 
%\end{description}
\end{abstract}

@@

The electrostatic nature of lipid molecules (a hydrophobic tail and a
hydrophilic head with an electric dipole) complicates the interactions
between a lipid bilayer membrane and another bilayer
membrane~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
Book_IntermolecularSurfaceForces, PerutkovaFrank-Bertoncelij2013_CSB} or
a solid (such as a glass substrate or a nano particle).  Adhesion
between a vesicle and a solid has been extensively studied with more
focus on the static equilibrium shapes~\cite{Seifert1990_PRA,BernardGuedeau-Boudeville2000_Langmuir,
ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,
GruhnFrankeDimova2007_Langmuir,das2008adhesion,
zhang2009phase,Agudo-Canalejo2015_ACSNano,Agudo-CanalejoLipowsky2015_NanoLett,
SteinkuhlerAgudo-Canalejo2016_BJ,Agudo-CanalejoLipowsky2017_SoftMatt}
than the transient adhesion process~\cite{cantat1999lift, suk-sei2001,
BlountMiksisDavis2013_PRSa}.  Adhesive interactions between lipid
membranes are essential in many biomedical, biological, and biophysical
processes.  For example, vesicle adhesion is crucial to initiate
membrane fusion and fission in endocytosis, exocytosis, and the
transport of small vesicles through membrane surfaces.  In the absence
of an external electric field and ions in the solvents, it is reported
that the adhesive interactions between two membranes can be well
approximated by the L.-J.-type
potential~\cite{FlormannAouane2017_SciReports}, that consists of a
long-range attraction component and a short-range repulsion
component~\cite{Book_IntermolecularSurfaceForces}, and the combination
of the two gives rise to an equilibrium distance where the interaction
potential is at its minimum~\cite{Book_IntermolecularSurfaceForces}.

The strength of membrane-membrane adhesion can be estimated through the
membrane contact angle at the edge of contact
zone~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir,
MaresDanielIglic2012_SciWorldJ}.  Alternatively, Evans and
Metcalfe~\cite{EvansMetcalfe1984_BJ} used the micropipette to measure
the adhesive force between two vesicles bound by strong adhesion.  They
were able to measure the reduction in the free energy per unit area of
membrane-membrane contact formation due to the van der Waals'
attraction. For the adhesive interaction between two lipid bilayer
membranes in buffer solutions, a typical range for the energy density is
between $1$ to $10$ $\mu J/m^2$, similar to the adhesion energy density
of $3$ $\mu J/m^2$ between two
RBCs~\cite{FlormannAouane2017_SciReports}.  For adhesion interaction
between a vesicle and a substrate~\cite{GruhnFrankeDimova2007_Langmuir},
the boundary between weak and strong adhesion is around $1$ $\mu J/m^2$:
the vesicle-substrate interaction is ``strong" when the adhesion energy
density is larger than $1$ $\mu J/m^2$ and ``weak" when the energy
density is less than $1$ $\mu J/m^2$.  
%In this work we use the ratio of
%the adhesion energy to the bending energy for classification of adhesion
%strength. 
The ratio of total adhesion energy to the bending energy
(bending rigidity of lipid bilayer membranes $\sim 10^{-19}$ $J$) gives
a measure of vesicle deformation in the presence of
adhesion~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.

@@

This paper is organized as follows. In Section~\ref{sec:ge} we formulate
our model for two-dimensional vesicle hydrodynamics with adhesive
interactions between membranes of distinct vesicles.  We simulate the
adhesion process of two vesicles in a quiescent flow in
Section~\ref{sec:qflow}, where we also present a simple lubrication
model to estimate how long it takes for two nearby vesicles to reach the
separation distance set by the adhesion potential.  In
Section~\ref{sec:eflow} we numerically investigate the hydrodynamics of
a vesicle doublet in a fluid trap where the stagnation point is actively
controlled to be at the center of the vesicle doublet. From these
results we propose a novel application of the microfluidic fluid trap to
probe the adhesion strength between lipid bilayer membranes in
solutions. In Section~\ref{sec:sflow} we investigate how two vesicles
may form a doublet as they move toward each other under a planar shear
flow.  We map out the parameter regions for bound/unbound vesicles under
a planar shear flow, and we also investigate the effects of adhesive
interactions on the rheological properties of a dilute suspension of
vesicle doublets.  Finally in Section~\ref{sec:conclusions} we discuss
the implications of our results and point out a few potential future
directions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations \label{sec:ge}}
We consider a suspension of locally inextensible vesicles in an
unbounded two-dimensional viscous fluid.  For simplicity, we assume the
fluid viscosity both inside and outside the vesicles is the same;
however, incorporating viscosity contrast is rather straightforward in
our numerical algorithm.  While we focus on a vesicle doublet suspension
for the rest of the paper, here we provide the most general formulation
for multiple vesicles interacting with each other through both
hydrodynamic and adhesive forces.  Individual vesicles are denoted as
$\gamma_j$, $j=1,\ldots,M$, and they are parameterized in arclength as
$\xx_j(s,t)$.  The union of all vesicles is denoted by $\gamma$.  Given
a background velocity $\uu_\infty$, the governing (dimensionless)
equations are
\begin{equation}
\begin{aligned}
  \mu \Delta \uu = \nabla p, \quad &\xx \in \RR^2,
    &&\mbox{\em conservation of momentum} \\
  \nabla \cdot \uu = 0, \quad &\xx \in \RR^2, 
    &&\mbox{\em conservation of mass} \\
  \uu \rightarrow \uu_\infty, \quad &\|\xx\| \rightarrow \infty,
    &&\mbox{\em far-field condition} \\
  \uu(\xx,t) = \dot{\xx}, \quad &\xx \in \gamma,
    &&\mbox{\em velocity continuity} \\
  \xx_s \cdot \uu_s =0, \quad &\xx \in \gamma,
    &&\mbox{\em local inextensibility} \\
  \llbracket T \rrbracket \nn = \xxi, \quad &\xx \in \gamma,
    &&\mbox{\em stress balance on membranes}
\end{aligned} \label{eq:gov}
\end{equation}
where $\uu$ is the fluid velocity field, $p$ is the pressure, and the scaled viscosity $\mu=1$ inside the vesicles. Outside the vesicle
$\mu=\mu_e/\mu_i$ with $\mu_i$ ($\mu_e$)  the viscosity of the interior  (exterior) fluid.  We set
the viscosity ratio $\mu_e/\mu_i=1$ for the rest of the paper.
$T = - p I + \mu\left(\nabla \uu + \nabla \uu^T\right)$ is the stress
tensor, $\llbracket T \rrbracket$ is the jump across the membrane, and
$\xxi$ is the traction that is the sum of the bending, stretching,
and adhesion forces defined in equation~(\ref{eqn:traction}) of Appendix \ref{sec:AppendixB}.  The bending force, arising from the Helfrich
energy model, is $\BB \xx = -\kappa_b \xx_{ssss}$, where the subscript $s$ denotes derivative with respect to arclength $s$. $\kappa_b$ is
the bending rigidity modulus which we set to be 1 for all examples. The
stretching force is $\TT \sigma = (\sigma \xx_s)_s$, where the tension,
$\sigma$, acts as a Lagrange multiplier to satisfy the local
extensibility constraint.  The resistance to bending and stretching are
standard assumptions on vesicles.  In this work, we include an adhesive
force, $\AA \xx$, that we now describe.

@@

The adhesion potential for a vesicle membrane has been modeled by a
L.-J.~type potential
%Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
%single three-dimensional vesicle and a solid wall at $z=0$.  They use
%the adhesion potential of the function form
\begin{align}
\label{eq:adhesion_potential}
  \phi(z) = \mathcal{H} \left[ 
    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
\end{align}
where $\mathcal{H}$ is the Hamaker constant and $\delta$ is the adhesion
length scale, and $z$ is the distance between a patch on the vesicle
membrane and a point on the other object, which could be another vesicle
membrane or a flat solid wall.  The characteristics of the
L.-J.~potential are summarized in Figure~\ref{fig:adhesionModel}(a): The
adhesive force is zero at the equilibrium distance $z=\delta$.  For
large distances ($z> \delta$) the adhesive potential is attractive while
for small distances ($z < \delta$) the potential is repulsive to prevent
physical contact.

@@

Focusing on intermediate adhesive strengths, we use Hamaker constants
ranging from $\mathcal{O}(10^{-1})$ to $\mathcal{O}(10^0)$ times the
bending rigidity modulus.  We assume that the adhesion force from
equation~\eqref{eq:adhesion_potential} applies between all pairs of
points on different vesicles, and in Appendix~\ref{sec:appendixA} the
net adhesive force at a point $\xx$ on vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}
This summation of adhesive forces is illustrated in
Figure~\ref{fig:adhesionModel}(b).  Figure~\ref{fig:adhesionModel}(c) is
an example of the calculated adhesive force projected onto their
center-of-mass vector. We notice that the adhesive force is repulsive in
the contact region, while for the rest of the membranes there is an
attractive force that acts to pull the two vesicles together. The
summary of boundary integral formulation can be found in
Appendix~\ref{sec:AppendixB}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Effects of the adhesion parameters on equilibrium
configuration of a vesicle pair}
\label{subsec:qflow_adhesion_parameters} We again simulate two identical
adhering vesicles with the adhesion force in equation~\eqref{eq:Fh}.
The initial vesicle separation is smaller than in the previous
simulations so that the equilibrium configuration is achieved in a
shorter time horizon.  Once a vesicle doublet is formed, the membrane
shape in the contact region depends on the adhesion strength relative to
the membrane bending rigidity.  For weak to moderate adhesion strength,
vesicle membranes are flattened in the contact region while the rest of
vesicle maintains a nearly spherical shape~\cite{EvansMetcalfe1984_BJ,
Book_PhysicalBasisCellAdhesion, Book_IntermolecularSurfaceForces,
RamachandranAndersonLealIsraelachvili2010_Langmuir}.  Under a strong
adhesion, however, the vesicle membranes in the contact region buckle
and form a sigmoidal shape that has also been observed in RBC
doublets~\cite{Ziherl2007_PRL, ZiherlSvetina2007_PNAS,
FlormannAouane2017_SciReports}.  An external electric field is also able
to buckle a vesicle membrane that is adhered to a solid
substrate~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.

@@

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
%  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
%  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
   \includegraphics[keepaspectratio=true,scale=0.45]{figs/Dec18_vesicle_shape_vs_rA_composite.png}
  \caption{\label{fig:Dec18_vesicle_shape} The equilibrium
  configurations of a doublet of identical vesicles under adhesion in a
  quiescent flow at three values of $\Delta A$.  The vesicle reduced
  areas of $\Delta A=0.95$, $0.75$, and $0.6$ are labeled.  The vesicle
  length is fixed at $2\pi$, the dimensionless bending rigidity modulus
  is $\kappa_b=1$, the Hamaker constant is $\mathcal{H}=5$, and the
  separation distance is $\delta=0.2$.  The color coding is the tension
  along the vesicle.  The overall equilibrium shapes of two vesicles
  under adhesive interactions vary with the reduced area.  The right
  figure shows the  membrane shapes in the contact region. The color
  coding is the adhesive force projected along the center-of-mass
  vector.} 
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a $(m,n) = (12,6)$
L.-J.~potential~\cite{FlormannAouane2017_SciReports}.  As the reduced
area decreases further, we observe undulation of the vesicle membrane on
the non-contact side while the contact region remains flat.  The color
coding along each curve is the tension of the vesicle membrane.  We
observe that the membrane tension in the contact region is very
negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.

@@

The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous
drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on
a planar extensional flow  where the fluid velocity field
$\uu=\dot\epsilon(-x,y)$ is centered at the origin ($(x,y)=(0,0)$), the
stagnation point where the fluid flow converges horizontally and
diverges vertically.  Placed symmetrically at the stagnation point of an
extensional flow, a single vesicle may remain steady and symmetric for
low extension rate $\dot\epsilon$.  For sufficiently large extension
rate $\dot\epsilon$ the vesicle may undergo asymmetric
deformation~\cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt},
similar to a surfactant-laden viscous drop under a planar extensional
flow~\cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.  To the
best of our knowledge, no studies on the interactions between two
vesicles in an extensional flow are available in the literature.  In the
following we first illustrate how two vesicles interact with each other
in a planar extensional flow. We then illustrate how the adhesion
strength between membranes can be measured non-intrusively by using the
fluid trap.

At the beginning of the first set of simulations (left panels in
Figure~\ref{fig:extensionalNonsymmetric}) we place a vesicle at
$(x,y)=(0,0)$, and the other vesicle at $(x,y) = (3,\Delta y)$ where the
initial vertical displacement $\Delta y$ varies from $\Delta y=0$ for
the top row, $\Delta y = 0.02$ for the second row, to $\Delta y =0.1$
for the bottom two rows in Figure~\ref{fig:extensionalNonsymmetric}.
The Hamaker constant is ${\cal H} = 0.7$ for the top three rows, and is
${\cal H} =0.6$ for the bottom row.  The color coding is the membrane
tension with the color bar on the right of each row. We note that the
negative tension in an extensional flow is consistent with the tension
for a vesicle with finite bending forces~\cite{Narsimhan2014_JFM} and
the speculation for a wrinkled membrane in the elongational
flow~\cite{KantslerSegreSteinberg2007_PRL}.

>>>>

\begin{abstract}
The dynamics of an adhesive two-dimensional vesicle doublet under
various flow conditions is investigated numerically using a high-order,
adaptive-in-time boundary integral method. In a quiescent flow, two
nearby vesicles move slowly towards each other under the adhesive
potential, pushing out fluid between them to form a vesicle doublet at
equilibrium. A lubrication analysis on such draining of a thin film
gives the dependencies of draining time on adhesion strength and
separation distance that are in good agreement with numerical results.
%
In a planar extensional flow we find a stable vesicle doublet forms only when two 
vesicles collide head-on around the stagnation point. 
In a microfluid trap where the stagnation of an extensional flow is
dynamically placed in the middle of a vesicle doublet through an active
control loop, novel dynamics of a vesicle doublet is observed. Numerical
simulations show that there exists a critical extensional flow rate
above which adhesive interaction is overcome by the diverging stream,
thus providing a simple method to measure the adhesion strength between
two vesicle membranes. 
%
In a planar shear flow, numerical simulations reveal that a vesicle
doublet may form provided that the adhesion strength is sufficiently
large at a given vesicle reduced area. 
Once a doublet is formed, its oscillatory dynamics is found to depend on the adhesion strength and their reduced area.
Furthermore the effective shear viscosity of a dilute suspension of vesicle doublets is
found to be a function of  reduced area.  Results from these numerical
studies and analysis shed light on the hydrodynamic and rheological
consequences of adhesive interactions between vesicles in a viscous
fluid.
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[PACS numbers]
%May be entered using the \verb+\pacs{#1}+ command.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item. 
%\end{description}
\end{abstract}

@@

The electrostatic nature of lipid molecules (a hydrophobic tail and a
hydrophilic head with an electric dipole) complicates the interactions
between a lipid bilayer membrane and another bilayer
membrane~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
Book_IntermolecularSurfaceForces, PerutkovaFrank-Bertoncelij2013_CSB} or
a solid (such as a glass substrate or a nano particle).  Adhesion
between a vesicle and a solid has been extensively studied with more
focus on the static equilibrium shapes~\cite{Seifert1990_PRA,BernardGuedeau-Boudeville2000_Langmuir,
ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,
GruhnFrankeDimova2007_Langmuir,das2008adhesion,
zhang2009phase,Agudo-Canalejo2015_ACSNano,Agudo-CanalejoLipowsky2015_NanoLett,
SteinkuhlerAgudo-Canalejo2016_BJ,Agudo-CanalejoLipowsky2017_SoftMatt}
than the transient adhesion process~\cite{cantat1999lift, suk-sei2001,
BlountMiksisDavis2013_PRSa}.  Adhesive interactions between lipid
membranes are essential in many biomedical, biological, and biophysical
processes.  For example, vesicle adhesion is crucial to initiate
membrane fusion and fission in endocytosis, exocytosis, and the
transport of small vesicles through membrane surfaces.  In the absence
of an external electric field and ions in the solvents, it is reported
that the adhesive interactions between two membranes can be well
approximated by the L.-J.-type
potential~\cite{FlormannAouane2017_SciReports}, that consists of a
long-range attraction component (truncated at some finite distance beyond which membrane interaction becomes negligible) 
and a short-range repulsion
component~\cite{Book_IntermolecularSurfaceForces}, and the combination
of the two gives rise to an equilibrium distance where the interaction
potential is at its minimum~\cite{Book_IntermolecularSurfaceForces}.

The strength of membrane-membrane adhesion can be estimated through the
membrane contact angle at the edge of contact
zone~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir,
MaresDanielIglic2012_SciWorldJ}.  Alternatively, Evans and
Metcalfe~\cite{EvansMetcalfe1984_BJ} used the micropipette to measure
the adhesive force between two vesicles bound by strong adhesion.  They
were able to measure the reduction in the free energy per unit area of
membrane-membrane contact formation due to the van der Waals'
attraction. For the adhesive interaction between two lipid bilayer
membranes in buffer solutions, a typical range for the energy density is
between $1$ to $10$ $\mu J/m^2$, similar to the adhesion energy density
of $3$ $\mu J/m^2$ between two
RBCs~\cite{FlormannAouane2017_SciReports}.  For adhesion interaction
between a vesicle and a substrate~\cite{GruhnFrankeDimova2007_Langmuir},
the boundary between weak and strong adhesion is around $1$ $\mu J/m^2$:
the vesicle-substrate interaction is ``strong" when the adhesion energy
density is larger than $1$ $\mu J/m^2$ and ``weak" when the energy
density is less than $1$ $\mu J/m^2$.  
%In this work we use the ratio of
%the adhesion energy to the bending energy for classification of adhesion
%strength. 
The ratio of total adhesion energy to the bending energy
(bending modulus of lipid bilayer membranes $\sim 10^{-19}$ $J$) gives
a measure of vesicle deformation in the presence of
adhesion~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.

@@

This paper is organized as follows. In Section~\ref{sec:ge} we formulate
our model for two-dimensional vesicle hydrodynamics with adhesive
interactions between membranes of distinct vesicles.  We simulate the
adhesion process of two vesicles in a quiescent flow in
Section~\ref{sec:qflow}, where we also present a simple lubrication
model to estimate how long it takes for two nearby vesicles to reach the
separation distance set by the adhesion potential.  In
Section~\ref{sec:eflow} we first study the hydrodynamics of two vesicles in
a planar extensional flow. We then numerically investigate the hydrodynamics of
a vesicle doublet in a fluid trap where the stagnation point is actively
controlled to be at the center of the vesicle doublet. From these
results we propose a novel application of the microfluidic fluid trap to
probe the adhesion strength between lipid bilayer membranes in
solutions. In Section~\ref{sec:sflow} we investigate how two vesicles
may form a doublet as they move toward each other under a planar shear
flow.  We map out the parameter regions for bound/unbound vesicles under
a planar shear flow, and we also investigate the effects of adhesive
interactions on the rheological properties of a dilute suspension of
vesicle doublets.  Finally in Section~\ref{sec:conclusions} we discuss
the implications of our results and point out a few potential future
directions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations \label{sec:ge}}
We consider a suspension of locally inextensible vesicles in an
unbounded two-dimensional viscous fluid.  For simplicity, we assume the
fluid viscosity both inside and outside the vesicles is the same;
however, incorporating viscosity contrast is rather straightforward in
our numerical algorithm.  While we focus on a vesicle doublet suspension
for the rest of the paper, here we provide the most general formulation
for multiple vesicles interacting with each other through both
hydrodynamic and adhesive forces.  Individual vesicles are denoted as
$\gamma_j$, $j=1,\ldots,M$, and they are parameterized in arclength as
$\xx_j(s,t)$.  The union of all vesicles is denoted by $\gamma$.  Given
a background velocity $\uu_\infty$, the governing (dimensionless)
equations are
\begin{equation}
\begin{aligned}
  \mu \Delta \uu = \nabla p, \quad &\xx \in \RR^2,
    &&\mbox{\em conservation of momentum} \\
  \nabla \cdot \uu = 0, \quad &\xx \in \RR^2, 
    &&\mbox{\em conservation of mass} \\
  \uu \rightarrow \uu_\infty, \quad &\|\xx\| \rightarrow \infty,
    &&\mbox{\em far-field condition} \\
  \uu(\xx,t) = \dot{\xx}, \quad &\xx \in \gamma,
    &&\mbox{\em velocity continuity} \\
  \xx_s \cdot \uu_s =0, \quad &\xx \in \gamma,
    &&\mbox{\em local inextensibility} \\
  \llbracket T \rrbracket \nn = \xxi, \quad &\xx \in \gamma,
    &&\mbox{\em stress balance on membranes}
\end{aligned} \label{eq:gov}
\end{equation}
where $\uu$ is the fluid velocity field, $p$ is the pressure, and the scaled viscosity $\mu=1$ inside the vesicles. Outside the vesicle
$\mu=\mu_e/\mu_i$ with $\mu_i$ ($\mu_e$)  the viscosity of the interior  (exterior) fluid.  We set
the viscosity ratio $\mu_e/\mu_i=1$ for the rest of the paper.
$T = - p I + \mu\left(\nabla \uu + \nabla \uu^T\right)$ is the stress
tensor, $\llbracket T \rrbracket$ is the jump across the membrane, and
$\xxi$ is the traction that is the sum of the bending, stretching,
and adhesion forces defined in equation~(\ref{eqn:traction}) of Appendix \ref{sec:AppendixB}.  The bending force, arising from the Helfrich
energy model, is $\BB \xx = -\kappa_b \xx_{ssss}$, where the subscript $s$ denotes derivative with respect to arclength $s$. $\kappa_b$ is
the bending modulus which we set to be 1 for all examples. The
stretching force is $\TT \sigma = (\sigma \xx_s)_s$, where the tension,
$\sigma$, acts as a Lagrange multiplier to satisfy the local
extensibility constraint.  The resistance to bending and stretching are
standard assumptions on vesicles.  In this work, we include an adhesive
force, $\AA \xx$, that we now describe.

@@

The adhesion potential for a vesicle membrane has been modeled by a
L.-J.~type potential
%Sukumaran and Seifert~\cite{suk-sei2001} consider adhesion between a
%single three-dimensional vesicle and a solid wall at $z=0$.  They use
%the adhesion potential of the function form
\begin{align}
\label{eq:adhesion_potential}
  \phi(z) = \mathcal{H} \left[ 
    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
\end{align}
where $\mathcal{H}$ is the Hamaker constant and $\delta$ is the adhesion
length scale, and $z$ is the distance between a patch on the vesicle
membrane and a point on the other object, which could be another vesicle
membrane or a flat solid wall.  The characteristics of the
L.-J.~potential are summarized in Figure~\ref{fig:adhesionModel}(a): The
adhesive force is zero at the equilibrium distance $z=\delta$.  For
large distances ($z> \delta$) the adhesive potential is attractive while
for small distances ($z < \delta$) the potential is repulsive to prevent
physical contact. The long-range attraction component should decay sufficiently fast
to mimic the finite-range attraction between RBCs. However, here to simplify
the formulation we do not introduce such a truncation in the attraction.

@@

Focusing on intermediate adhesive strengths, we use Hamaker constants
ranging from $\mathcal{O}(10^{-1})$ to $\mathcal{O}(10^0)$ times the
bending modulus.  We assume that the adhesion force from
equation~\eqref{eq:adhesion_potential} applies between all pairs of
points on different vesicles, and in Appendix~\ref{sec:appendixA} the
net adhesive force at a point $\xx$ on vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}
This summation of adhesive forces is illustrated in
Figure~\ref{fig:adhesionModel}(b).  Figure~\ref{fig:adhesionModel}(c) is
an example of the calculated adhesive force projected onto their
center-of-mass vector. We notice that the adhesive force is repulsive in
the contact region, while for the rest of the membranes there is an
attractive force that acts to pull the two vesicles together. The
summary of boundary integral formulation can be found in
Appendix~\ref{sec:AppendixB}. For the rest of the paper, 
the dimensionless bending modulus is set to be one ($\kappa_b = 1$) unless otherwise specified.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Effects of the adhesion parameters on equilibrium
configuration of a vesicle pair}
\label{subsec:qflow_adhesion_parameters} We again simulate two identical
adhering vesicles with the adhesion force in equation~\eqref{eq:Fh}.
The initial vesicle separation is smaller than in the previous
simulations so that the equilibrium configuration is achieved in a
shorter time horizon.  Once a vesicle doublet is formed, the membrane
shape in the contact region depends on the adhesion strength relative to
the membrane bending modulus.  For weak to moderate adhesion strength,
vesicle membranes are flattened in the contact region while the rest of
vesicle maintains a nearly spherical shape~\cite{EvansMetcalfe1984_BJ,
Book_PhysicalBasisCellAdhesion, Book_IntermolecularSurfaceForces,
RamachandranAndersonLealIsraelachvili2010_Langmuir}.  Under a strong
adhesion, however, the vesicle membranes in the contact region buckle
and form a sigmoidal shape that has also been observed in RBC
doublets~\cite{Ziherl2007_PRL, ZiherlSvetina2007_PNAS,
FlormannAouane2017_SciReports}.  An external electric field is also able
to buckle a vesicle membrane that is adhered to a solid
substrate~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.

@@

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
%  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
%  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
   \includegraphics[keepaspectratio=true,scale=0.45]{figs/Dec18_vesicle_shape_vs_rA_composite.png}
  \caption{\label{fig:Dec18_vesicle_shape} The equilibrium
  configurations of a doublet of identical vesicles under adhesion in a
  quiescent flow at three values of $\Delta A$.  The vesicle reduced
  areas of $\Delta A=0.95$, $0.75$, and $0.6$ are labeled.  The vesicle
  length is fixed at $2\pi$, the dimensionless bending modulus
  $\kappa_b=1$, the Hamaker constant $\mathcal{H}=5$, and the
  separation distance $\delta=0.2$.  The color coding is the tension
  along the vesicle.  The overall equilibrium shapes of two vesicles
  under adhesive interactions vary with the reduced area.  The right
  figure shows the  membrane shapes in the contact region. The color
  coding is the adhesive force projected along the center-of-mass
  vector.} 
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a $(m,n) = (12,6)$
L.-J.~potential~\cite{FlormannAouane2017_SciReports}.  As the reduced
area decreases further, we observe undulation of the vesicle membrane on
the non-contact side while the contact region remains flat.  The color
coding along each curve is the tension of the vesicle membrane.  We
observe that the membrane tension in the contact region is very
negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.

@@

The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous
drop~\cite{KantslerSegreSteinberg2007_PRL,KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on
a planar extensional flow  where the fluid velocity field
$\uu=\dot\epsilon(-x,y)$ is centered at the origin ($(x,y)=(0,0)$), the
stagnation point where the fluid flow converges horizontally and
diverges vertically.  Placed symmetrically at the stagnation point of an
extensional flow, a single vesicle may remain steady and symmetric for
low extension rate $\dot\epsilon$.  For sufficiently large extension
rate $\dot\epsilon$ the vesicle may undergo asymmetric
deformation~\cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt},
similar to a surfactant-laden viscous drop under a planar extensional
flow~\cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.  To the
best of our knowledge, no studies on the interactions between two
vesicles in an extensional flow are available in the literature.  In the
following we first illustrate how two vesicles interact with each other
in a planar extensional flow. We then illustrate how the adhesion
strength between membranes can be measured non-intrusively by using the
fluid trap.

At the beginning of the first set of simulations (left panels in
Figure~\ref{fig:extensionalNonsymmetric}) we place a vesicle at
$(x,y)=(0,0)$, and the other vesicle at $(x,y) = (3,\Delta y)$ where the
initial vertical displacement $\Delta y$ varies from $\Delta y=0$ for
the top row, $\Delta y = 0.02$ for the second row, to $\Delta y =0.1$
for the bottom two rows in Figure~\ref{fig:extensionalNonsymmetric}.
The Hamaker constant is ${\cal H} = 0.7$ for the top three rows, and is
${\cal H} =0.6$ for the bottom row.  The color coding is the membrane
tension with the color bar on the right of each row. We note that the
negative tension in an extensional flow is consistent with the destabilizing tension 
for a vesicle with finite bending forces~\cite{Narsimhan2014_JFM}.
%and the speculation for a wrinkled membrane in the elongational flow~\cite{KantslerSegreSteinberg2007_PRL}.
